Improving \textsl{Gaia} parallaxes with a data-driven model of the color--magnitude diagram

### 2017-02-22 paperDistance/paper.tex
start discussion; need to make dinner now

\section{Discussion}
What have we achieved and why is it important?

>>>>

\section{Discussion}

We have shown that it is possible to obtain photometric parallaxes for distant
stars in the \gaia\ data without any use of physical stellar models.
Although we have not performed principled Bayesian inference in this project,
we have performed a statistically responsible deconvolution of the
\gaia\ \tgas\ data that is justifiable under a clear set of assumptions.
...DWH NOT DONE THIS PARAGRAPH

What have we achieved and why is it important?
